---
title: "Lab1"
author: "Claudius Taylor"
date: "9/1/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Generating random variables
```{r}
a <- rnorm(10,0,1)
b <- rnorm(50,0,1)
c <- rnorm(100,0,1)
d <- rnorm(1000,0,1)
```

## Estimating first 10 autocovarinace, autocorrelation and plotting the trajectories and correlogram
```{r}
acf(a)
plot(a,type='l',ylab="White Noise",frame.plot=FALSE)

acf(b,10)
plot(b,type='l',ylab="White Noise",frame.plot=FALSE)

acf(c,10)
plot(c,type='l',ylab="White Noise",frame.plot=FALSE)

acf(d,10)
plot(d,type='l',ylab="White Noise",frame.plot=FALSE)
```

## Generating random variables for 
$$ N(0, \sigma^2 \neq 1) $$

```{r}
aa <- rnorm(10,0,2)
bb <- rnorm(50,0,2)
cc <- rnorm(100,0,2)
dd <- rnorm(1000,0,2)
```

## Estimating first 10 autocovarinace, autocorrelation and plotting the trajectories and correlogram
```{r}
acf(aa,10)
plot(aa,type='l',ylab="White Noise",frame.plot=FALSE)

acf(bb,10)
plot(bb,type='l',ylab="White Noise",frame.plot=FALSE)

acf(cc,10)
plot(cc,type='l',ylab="White Noise",frame.plot=FALSE)

acf(dd,10)
plot(dd,type='l',ylab="White Noise",frame.plot=FALSE)
```

## It can be concluded that the significance bounds (confidence limits) becomes narrower as n increases from n = 10, 50, 100, 1000. Also Lag 0 equals 1 for all variables. Values outside the limits are considered to have significant correlation. The correlogram does not change for variance not equal to 1.
