---
title: "Lab3"
author: "Claudius Taylor"
date: "September 15, 2018"
output: pdf_document
---

```{r results='asis', echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(TSA)
library(dplyr)
library(astsa)
library(tseries)
```

## 1. For SOI data, calculate the 95% bounds for the autocorrelation.

```{r}
data(soi)
upbound <- 1.96*1/sqrt(length(soi))
upbound
lowbound <- -1.96*1/sqrt(length(soi))
lowbound
```

## 2. Verify your results in 1 by superimposing those bounds on the corresponding correlogram.

```{r}
acf(soi, type = "correlation")
abline(h=1.96/sqrt(459),col="red")
abline(h=-1.96/sqrt(459),col="red")
```

## 3. Consider two data sets: oil and gas from astsa package. Are any of these datasets stationary? Why or why not?

```{r}
ts.plot(oil)
acf(oil, type = "correlation")
ts.plot(gas)
acf(gas, type = "correlation")
```

### Both oil and gas datasets are not stationary, as there acf plot decays gradually as lag increases.

## 4. Apply the transformation $$\nabla logX_t$$ , where $$\nabla y_t = y_t - y_{t-1}$$ to both data sets. Are any of these dataset stationary? Why or why not?


```{r}
oil_trans <- diff(log(oil))
gas_trans <- diff(log(gas))
acf(oil_trans, type = "correlation", lag.max = "m")
acf(gas_trans, type = "correlation", lag.max = "m")
```

### The transformed data for oil and gas appears to be somewhat staionary now. 

## 5. Produce a cross-correlation plot for the transformed data.

```{r}
ccf(oil_trans, gas_trans, ylab='CCorrF', type = "correlation")
```

### Both transformed data for oil and gas evolve concurrently. The correlation is nonetheless strong around 0.62.
